---
title: "Conditioned Reinforcement"
author: "Marios Panayi"
date: "12/28/2020"
output: word_document
---

```{r setup, include=FALSE, message = FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE)
## Packages for data organisation and plotting
library(tidyverse)
# Package for relative file paths
library(here)
# library(ggpubr)
library(cowplot)
library(ggsignif)
library(patchwork)
################################################################################
## Packages for Data analysis
library(afex)
afex_options(emmeans_model = "multivariate")# use multivariate model for all follow-up tests.
library(emmeans)
# install.packages("devtools")
# devtools::install_github("crsh/papaja")
library(papaja)
library(knitr)
# remotes::install_github("noamross/redoc")
# library(redoc)
```



```{r Load data from figures for Stats , include=FALSE, message = FALSE, warning=FALSE}
CRF_Acquisition_CSPre <- read_csv(here("figures","figure_data","CRF_Acquisition_CSPre.csv"))
CRF_Acquisition_CSPre_Last5s <- read_csv(here("figures","figure_data","CRF_Acquisition_CSPre_Last5s.csv"))
# Test Data
# CRF_data_P100_HighvsLow_long <- read_csv(here("figures","figure_data","CRF_data_P100_HighvsLow_long.csv"))
# CRF_data_P50_HighvsLow_long <- read_csv(here("figures","figure_data","CRF_data_P50_HighvsLow_long.csv"))
# CRF_data_High_100Vs50_long <- read_csv(here("figures","figure_data","CRF_data_High_100Vs50_long.csv"))
# CRF_data_Low_100Vs50_long <- read_csv(here("figures","figure_data","CRF_data_Low_100Vs50_long.csv"))
CRF_ALL_data_long_Avg <- read_csv(here("figures","figure_data","CRF_ALL_data_long_Avg.csv"))


```



```{r Stage 1 Acquisition STats , include=FALSE, message = FALSE, warning=FALSE}
rawdata <- CRF_Acquisition_CSPre %>% 
  filter(Period == "CS")
# Stage 1 Acquisition Frequency
anova <- aov_4(MagEntries ~ (Day*CS_name|subject), data = rawdata, anova_table = list(correction = "none", es = "pes"))
anova_Stg1_Freq <- apa_print(anova, mse = "FALSE",correction = "none",es = "pes")
## simple effects - linear trend on Day
simple <- emmeans(anova, ~CS_name)
simple_Stg1_Freq <- apa_print(contrast(simple, interaction = "pairwise", adjust = "tukey"))

anova_Stg1_Freq$table
simple_Stg1_Freq$table


# Stage 1 Acquisition Duration
anova <- aov_4(MagDuration ~ (Day*CS_name|subject), data = rawdata, anova_table = list(correction = "none", es = "pes"))
anova_Stg1_Dur <- apa_print(anova, mse = "FALSE",correction = "none",es = "pes")
## simple effects - linear trend on Day
simple <- emmeans(anova, ~CS_name)
simple_Stg1_Dur <- apa_print(contrast(simple, interaction = "pairwise", adjust = "tukey"))

anova_Stg1_Dur$table
simple_Stg1_Dur$table

```



```{r Stage 1 Acquisition STats Mag*prob , include=FALSE, message = FALSE, warning=FALSE}
rawdata <- CRF_Acquisition_CSPre %>% 
  filter(Period == "CS",
         Day < 7)
# Stage 1 Acquisition Frequency
anova <- aov_4(MagEntries ~ (Day*magnitude*probability|subject), data = rawdata, anova_table = list(correction = "none", es = "pes"))
anova_Stg1_Freq <- apa_print(anova, mse = "FALSE",correction = "none",es = "pes")
## simple effects - linear trend on Day
simple <- emmeans(anova, ~Day*probability)
simple_Stg1_Freq <- apa_print(contrast(simple, interaction = "poly", by = "probability", adjust = "tukey"))

anova_Stg1_Freq$table
simple_Stg1_Freq$table


# Stage 1 Acquisition Duration
anova <- aov_4(MagDuration ~ (Day*magnitude*probability|subject), data = rawdata, anova_table = list(correction = "none", es = "pes"))
anova_Stg1_Dur <- apa_print(anova, mse = "FALSE",correction = "none",es = "pes")
## simple effects - linear trend on Day
simple <- emmeans(anova, ~Day*probability)
simple_Stg1_Dur <- apa_print(contrast(simple, interaction = "pairwise", by = "Day", adjust = "tukey"))

anova_Stg1_Dur$table
simple_Stg1_Dur$table
```


`r apa_table(within(anova_Stg1_Freq$table, rm(pes)),caption = "Magazine Frequency ANOVA")`



`r apa_table(within(anova_Stg1_Dur$table, rm(pes)),caption = "Magazine Duration ANOVA")`


```{r Stage 1 Acquisition Last 5s Stats , include=FALSE, message = FALSE, warning=FALSE}
rawdata <- CRF_Acquisition_CSPre_Last5s %>% 
  filter(Period == "CS",
         Day < 7)
# Stage 1 Acquisition Frequency
anova <- aov_4(MagEntries ~ (Day*CS_name|subject), data = rawdata, anova_table = list(correction = "none", es = "pes"))
anova_Stg1_Freq_5s <- apa_print(anova, mse = "FALSE",correction = "none",es = "pes")
## simple effects - linear trend on Day
simple <- emmeans(anova, ~CS_name)
simple_Stg1_Freq_5s <- apa_print(contrast(simple, interaction = "pairwise", adjust = "tukey"))

anova_Stg1_Freq_5s$table
simple_Stg1_Freq_5s$table


# Stage 1 Acquisition Duration
anova <- aov_4(MagDuration ~ (Day*CS_name|subject), data = rawdata, anova_table = list(correction = "none", es = "pes"))
anova_Stg1_Dur_5s <- apa_print(anova, mse = "FALSE",correction = "none",es = "pes")
## simple effects - linear trend on Day
simple <- emmeans(anova, ~CS_name)
simple_Stg1_Dur_5s <- apa_print(contrast(simple, interaction = "pairwise", adjust = "tukey"))

anova_Stg1_Dur_5s$table
simple_Stg1_Dur_5s$table
```




```{r Stage 1 Acquisition Last 5s Stats mag*prob , include=FALSE, message = FALSE, warning=FALSE}
rawdata <- CRF_Acquisition_CSPre_Last5s %>% 
  filter(Period == "CS")
# Stage 1 Acquisition Frequency
anova <- aov_4(MagEntries ~ (Day*magnitude*probability|subject), data = rawdata, anova_table = list(correction = "none", es = "pes"))
anova_Stg1_Freq_5s <- apa_print(anova, mse = "FALSE",correction = "none",es = "pes")
## simple effects - linear trend on Day
simple <- emmeans(anova, ~magnitude*probability)
simple_Stg1_Freq_5s <- apa_print(contrast(simple, interaction = "pairwise", by = "probability", adjust = "tukey"))

anova_Stg1_Freq_5s$table
simple_Stg1_Freq_5s$table


# Stage 1 Acquisition Duration
anova <- aov_4(MagDuration ~ (Day*magnitude*probability|subject), data = rawdata, anova_table = list(correction = "none", es = "pes"))
anova_Stg1_Dur_5s <- apa_print(anova, mse = "FALSE",correction = "none",es = "pes")
## simple effects - linear trend on Day
simple <- emmeans(anova, ~magnitude*probability)
simple_Stg1_Dur_5s <- apa_print(contrast(simple, interaction = "pairwise",  by = "probability", adjust = "tukey"))

anova_Stg1_Dur_5s$table
simple_Stg1_Dur_5s$table
```


`r apa_table(within(anova_Stg1_Freq_5s$table, rm(pes)),caption = "Magazine Frequency ANOVA - 5s")`



`r apa_table(within(anova_Stg1_Dur_5s$table, rm(pes)),caption = "Magazine Duration ANOVA - 5s")`

```{r Stage 3 Enhanced Acquisition Stats Mag*prob , include=FALSE, message = FALSE, warning=FALSE}
rawdata <- CRF_Acquisition_CSPre %>% 
  filter(Period == "CSPre",
         Day >= 22)
# Stage 1 Acquisition Frequency
anova <- aov_4(MagEntries ~ (Day*magnitude*probability|subject), data = rawdata, anova_table = list(correction = "none", es = "pes"))
anova_Stg3_Freq <- apa_print(anova, mse = "FALSE",correction = "none",es = "pes")
## simple effects - linear trend on Day
simple <- emmeans(anova, ~magnitude*probability)
simple_Stg3_Freq <- apa_print(contrast(simple, interaction = "pairwise", by = "magnitude", adjust = "none"))
simple_Stg3_Freq2 <- apa_print(contrast(simple, interaction = "pairwise", by = "probability", adjust = "none"))

anova_Stg3_Freq$table
simple_Stg3_Freq$table
simple_Stg3_Freq2$table

# Stage 1 Acquisition Duration
anova <- aov_4(MagDuration ~ (Day*magnitude*probability|subject), data = rawdata, anova_table = list(correction = "none", es = "pes"))
anova_Stg3_Dur <- apa_print(anova, mse = "FALSE",correction = "none",es = "pes")
## simple effects - linear trend on Day
simple <- emmeans(anova, ~Day*magnitude)
simple_Stg3_Dur <- apa_print(contrast(simple, interaction = "pairwise", by = "Day", adjust = "tukey"))

anova_Stg3_Dur$table
simple_Stg3_Dur$table
```


#Enhanced Acquisition Only

`r apa_table(within(anova_Stg3_Freq$table, rm(pes)),caption = "Magazine Frequency ANOVA")`

*Simple Effects*

`r apa_table(simple_Stg3_Freq$table)`

*Simple Effects*
`r apa_table(simple_Stg3_Freq2$table)`

`r apa_table(within(anova_Stg3_Dur$table, rm(pes)),caption = "Magazine Duration ANOVA")`


```{r Test CRF DIfference Scores Stats , include=FALSE, message = FALSE, warning=FALSE}
# This analysis is not great - Standard ANOVA, only 4 rats did all 4 tests so this analysis kicks out too many subjects
rawdata <- CRF_ALL_data_long_Avg %>% 
  filter(Value == "Diff",
         measure == "LP",
         ExcludeSubject == "Keep")
# Stage 1 Acquisition Frequency
anova <- aov_4(Freq ~ (TestCondition|subject), data = rawdata, anova_table = list(correction = "none", es = "pes"))
anova_test_Value <- apa_print(anova, mse = "FALSE",correction = "none",es = "pes")
# ## simple effects - linear trend on Day
# simple <- emmeans(anova, ~TestCondition)
# simple_Test_Value <- apa_print(contrast(simple, interaction = "pairwise", by = "Probability", adjust = "tukey"))

anova_test_Value$table
# simple_Test_Value$table


```



