---
title: "LY354740_aFCV_stats"
author: "Marios Panayi"
date: "4/16/2020"
output: word_document
---

```{r setup, include=FALSE, message = FALSE, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE)
## Packages for data organisation and plotting
library(tidyverse)
#library(ggpubr)
library(cowplot)
################################################################################
## Packages for Data analysis
library(afex)
afex_options(emmeans_model = "multivariate") # use multivariate model for all follow-up tests.
library(emmeans)
# install.packages("devtools")
# devtools::install_github("crsh/papaja")
library(papaja)
library(knitr)
#Read in the data as global variable
full_data <- read_csv("../rawdata/Anaesthetized_rawdata.csv")

```

# Statistical Analysis

Standard Repeated measures ANOVA (Drug between groups, stimulation paramaters within subjects), Tukey post-hoc correction applied for all follow up tests..

# Raw Data 
 
## Pre vs Post Drug analysis - Baseline periods

```{r Pre vs post injection DA_Max, echo=FALSE,message = FALSE, include=FALSE, warning=FALSE}

#Filter the relevant stage of data for analysis
data_subset <- full_data %>% 
  filter(ExperimentalStage == "04_Baseline2_Pre" | ExperimentalStage == "05_Baseline_Post") %>% 
  separate(ExperimentalStage, c("stagenumber", "stagename", "injectiontime"))

anova <- aov_4(DA_max ~ drugs + (injectiontime|subj), data = data_subset, anova_table = list(correction = "none", es = "pes"))

anova_print <- apa_print(anova, mse = "FALSE",correction = "none",es = "pes")

```

Peak DA decreased from pre- to post-injection (Period `r anova_print$statistic$injectiontime`), however this was not significantly modulated by LY3454740 or Saline (Drug `r anova_print$statistic$drugs`; Drug x Period `r anova_print$statistic$drugs_injectiontime`).

```{r Pre vs post injection DA_AUC, echo=FALSE,message = FALSE, include=FALSE, warning=FALSE}

#Filter the relevant stage of data for analysis
data_subset <- full_data %>% 
  filter(ExperimentalStage == "04_Baseline2_Pre" | ExperimentalStage == "05_Baseline_Post") %>% 
  separate(ExperimentalStage, c("stagenumber", "stagename", "injectiontime"))

anova <- aov_4(DA_AUC ~ drugs + (injectiontime|subj), data = data_subset, anova_table = list(correction = "none", es = "pes"))

anova_print <- apa_print(anova, mse = "FALSE",correction = "none",es = "pes")

```

AUC was not significantly modulated by LY3454740 or Saline (Drug `r anova_print$statistic$drugs`; Period `r anova_print$statistic$injectiontime`; Drug x Period `r anova_print$statistic$drugs_injectiontime`).


```{r Pre vs post injection DA_Latency_s, echo=FALSE,message = FALSE, include=FALSE, warning=FALSE}

#Filter the relevant stage of data for analysis
data_subset <- full_data %>% 
  filter(ExperimentalStage == "04_Baseline2_Pre" | ExperimentalStage == "05_Baseline_Post") %>% 
  separate(ExperimentalStage, c("stagenumber", "stagename", "injectiontime"))

anova <- aov_4(DA_Latency_s ~ drugs + (injectiontime|subj), data = data_subset, anova_table = list(correction = "none", es = "pes"))

anova_print <- apa_print(anova, mse = "FALSE",correction = "none",es = "pes")

```

Latency to peak DA was not significantly modulated by LY3454740 or Saline (Drug `r anova_print$statistic$drugs`; Period `r anova_print$statistic$injectiontime`; Drug x Period `r anova_print$statistic$drugs_injectiontime`).



```{r Pre vs post injection t50_s, echo=FALSE,message = FALSE, include=FALSE, warning=FALSE}
#Load t50 data - only including extimates where Rsquared > 0.8
data_subset <- read_csv("../rawdata/Anaesthetized_rawdata_t50.csv")
#Filter the relevant stage of data for analysis
data_subset <- data_subset %>% 
  filter(ExperimentalStage == "04_Baseline2_Pre" | ExperimentalStage == "05_Baseline_Post") %>% 
  separate(ExperimentalStage, c("stagenumber", "stagename", "injectiontime"))

anova <- aov_4(t50_s ~ drugs + (injectiontime|subj), data = data_subset, anova_table = list(correction = "none", es = "pes"))

anova_print <- apa_print(anova, mse = "FALSE",correction = "none",es = "pes")

```

DA reuptake (as indexed by t50 point)  was not significantly modulated by LY3454740 or Saline ( Period `r anova_print$statistic$injectiontime`; Drug x Period `r anova_print$statistic$drugs_injectiontime`). Overall, DA reuptake was slower overall in animals asigned to the Saline group, but this failed to reach significance (Drug `r anova_print$statistic$drugs`).


## Pre Drug

### Stimulation Intensity Response Curve

```{r 02_StimIntensity_Pre DA_Max, echo=FALSE,message = FALSE, include=FALSE, warning=FALSE}

#Filter the relevant stage of data for analysis
data_subset_ <- full_data %>% 
  filter(ExperimentalStage == "02_StimIntensity_Pre")

anova <- aov_4(DA_max ~ drugs + (stimStrength|subj), data = data_subset, anova_table = list(correction = "none", es = "pes"))

anova_print_Intensity_Pre_Peak <- apa_print(anova, mse = "FALSE",correction = "none",es = "pes")


simple <- emmeans(anova, ~stimStrength)
simple_print_Intensity_Pre_Peak <- apa_print.emmGrid(pairs(simple, adjust = "tukey"))


```

Peak DA increased with stimulation intensity (Intensity: `r anova_print_Intensity_Pre_Peak$statistic$stimStrength`; 100 vs 200 `r simple_print_Intensity_Pre_Peak$statistic$X100_X200`, 200 vs 300 `r simple_print_Intensity_Pre_Peak$statistic$X200_X300`), but was not modulated by drug condition (Drug: `r anova_print_Intensity_Pre_Peak$statistic$drugs`, Drug x Intensity: `r anova_print_Intensity_Pre_Peak$statistic$drugs_stimStrength`).

```{r 02_StimIntensity_Pre DA_AUC, echo=FALSE,message = FALSE, include=FALSE, warning=FALSE}

#Filter the relevant stage of data for analysis
data_subset <- full_data %>% 
  filter(ExperimentalStage == "02_StimIntensity_Pre")

anova <- aov_4(DA_AUC ~ drugs + (stimStrength|subj), data = data_subset, anova_table = list(correction = "none", es = "pes"))

anova_print_Intensity_Pre_AUC <- apa_print(anova, mse = "FALSE",correction = "none",es = "pes")


simple <- emmeans(anova, ~stimStrength)
simple_print_Intensity_Pre_AUC <- apa_print.emmGrid(pairs(simple, adjust = "tukey"))


```

Similarly, AUC increased with stimulation intensity (Intensity: `r anova_print_Intensity_Pre_AUC$statistic$stimStrength`; 100 vs 200 `r simple_print_Intensity_Pre_AUC$statistic$X100_X200`, 200 vs 300 `r simple_print_Intensity_Pre_AUC$statistic$X200_X300`), but was not modulated by drug condition (Drug: `r anova_print_Intensity_Pre_AUC$statistic$drugs`, Drug x Intensity: `r anova_print_Intensity_Pre_AUC$statistic$drugs_stimStrength`).

```{r 02_StimIntensity_Pre DA_Latency_s, echo=FALSE,message = FALSE, include=FALSE, warning=FALSE}

#Filter the relevant stage of data for analysis
data_subset <- full_data %>% 
  filter(ExperimentalStage == "02_StimIntensity_Pre")

anova <- aov_4(DA_Latency_s ~ drugs + (stimStrength|subj), data = data_subset, anova_table = list(correction = "none", es = "pes"))

anova_print_Intensity_Pre_Latency <- apa_print(anova, mse = "FALSE",correction = "none",es = "pes")


simple <- emmeans(anova, ~stimStrength)
simple_print_Intensity_Pre_Latency <- apa_print.emmGrid(pairs(simple, adjust = "tukey"))


```

Latency to peak was not modulated by stimulation intensity (Intensity: `r anova_print_Intensity_Pre_Latency$statistic$stimStrength`, or by drug condition (Drug: `r anova_print_Intensity_Pre_Latency$statistic$drugs`, Drug x Intensity: `r anova_print_Intensity_Pre_Latency$statistic$drugs_stimStrength`).



### Stimulation Pulse Number Response Curve


```{r 03_StimPulse_Pre DA_Max, echo=FALSE,message = FALSE, include=FALSE, warning=FALSE}

#Filter the relevant stage of data for analysis
data_subset <- full_data %>% 
  filter(ExperimentalStage == "03_StimPulse_Pre")

anova <- aov_4(DA_max ~ drugs + (stimPulses|subj), data = data_subset, anova_table = list(correction = "none", es = "pes"))

anova_print_Pulses_Pre_Peak <- apa_print(anova, mse = "FALSE",correction = "none",es = "pes")


simple <- emmeans(anova, ~stimPulses)
simple_print_Pulses_Pre_Peak <- apa_print.emmGrid(pairs(simple, adjust = "tukey"))


```

Peak DA increased with pulse number (Pulses: `r anova_print_Pulses_Pre_Peak$statistic$stimPulses`; 12 vs 24 `r simple_print_Pulses_Pre_Peak$statistic$X12_X24`, 24 vs 36 `r simple_print_Pulses_Pre_Peak$statistic$X24_X36`), but was not modulated by drug condition (Drug: `r anova_print_Pulses_Pre_Peak$statistic$drugs`, Drug x Intensity: `r anova_print_Pulses_Pre_Peak$statistic$drugs_stimPulses`).

```{r 03_StimPulse_Pre DA_AUC, echo=FALSE,message = FALSE, include=FALSE, warning=FALSE}

#Filter the relevant stage of data for analysis
data_subset <- full_data %>% 
  filter(ExperimentalStage == "03_StimPulse_Pre")

anova <- aov_4(DA_AUC ~ drugs + (stimPulses|subj), data = data_subset, anova_table = list(correction = "none", es = "pes"))

anova_print_Pulses_Pre_AUC <- apa_print(anova, mse = "FALSE",correction = "none",es = "pes")


simple <- emmeans(anova, ~stimPulses)
simple_print_Pulses_Pre_AUC <- apa_print.emmGrid(pairs(simple, adjust = "tukey"))


```

Similarly, AUC increased with stimulation intensity (Pulses: `r anova_print_Pulses_Pre_AUC$statistic$stimPulses`; 12 vs 24 `r simple_print_Pulses_Pre_AUC$statistic$X12_X24`, 24 vs 36 `r simple_print_Pulses_Pre_AUC$statistic$X24_X36`), but was not modulated by drug condition (Drug: `r anova_print_Pulses_Pre_AUC$statistic$drugs`, Drug x Intensity: `r anova_print_Pulses_Pre_AUC$statistic$drugs_stimPulses`).

```{r 03_StimPulse_Pre DA_Latency_s, echo=FALSE,message = FALSE, include=FALSE, warning=FALSE}

#Filter the relevant stage of data for analysis
data_subset <- full_data %>% 
  filter(ExperimentalStage == "03_StimPulse_Pre")

anova <- aov_4(DA_Latency_s ~ drugs + (stimPulses|subj), data = data_subset, anova_table = list(correction = "none", es = "pes"))

anova_print_Pulses_Pre_Latency <- apa_print(anova, mse = "FALSE",correction = "none",es = "pes")


simple <- emmeans(anova, ~stimPulses)
simple_print_Pulses_Pre_Latency <- apa_print.emmGrid(pairs(simple, adjust = "tukey"))



```

Latency to peak was also modulated by stimulation intensity (Pulses: `r anova_print_Pulses_Pre_Latency$statistic$stimPulses`; 12 vs 24 `r simple_print_Pulses_Pre_Latency$statistic$X12_X24`, 24 vs 36 `r simple_print_Pulses_Pre_Latency$statistic$X24_X36`), but was not modulated by drug condition (Drug: `r anova_print_Pulses_Pre_Latency$statistic$drugs`, Drug x Intensity: `r anova_print_Pulses_Pre_Latency$statistic$drugs_stimPulses`).



## Post Drug

### Stimulation Intensity Response Curve

```{r 06_StimIntensity_Post DA_Max, echo=FALSE,message = FALSE, include=FALSE, warning=FALSE}

#Filter the relevant stage of data for analysis
data_subset <- full_data %>% 
  filter(ExperimentalStage == "06_StimIntensity_Post")

anova <- aov_4(DA_max ~ drugs + (stimStrength|subj), data = data_subset, anova_table = list(correction = "none", es = "pes"))

anova_print_Intensity_Post_Peak <- apa_print(anova, mse = "FALSE",correction = "none",es = "pes")


simple <- emmeans(anova, ~stimStrength)
simple_print_Intensity_Post_Peak <- apa_print.emmGrid(pairs(simple, adjust = "tukey"))


```

Peak DA increased with stimulation intensity (Intensity: `r anova_print_Intensity_Post_Peak$statistic$stimStrength`; 100 vs 200 `r simple_print_Intensity_Post_Peak$statistic$X100_X200`, 200 vs 300 `r simple_print_Intensity_Post_Peak$statistic$X200_X300`), but was not modulated by drug condition (Drug: `r anova_print_Intensity_Post_Peak$statistic$drugs`, Drug x Intensity: `r anova_print_Intensity_Post_Peak$statistic$drugs_stimStrength`).

```{r 06_StimIntensity_Post DA_AUC, echo=FALSE,message = FALSE, include=FALSE, warning=FALSE}

#Filter the relevant stage of data for analysis
data_subset <- full_data %>% 
  filter(ExperimentalStage == "06_StimIntensity_Post")

anova <- aov_4(DA_AUC ~ drugs + (stimStrength|subj), data = data_subset, anova_table = list(correction = "none", es = "pes"))

anova_print_Intensity_Post_AUC <- apa_print(anova, mse = "FALSE",correction = "none",es = "pes")


simple <- emmeans(anova, ~stimStrength)
simple_print_Intensity_Post_AUC <- apa_print.emmGrid(pairs(simple, adjust = "tukey"))



```

Similarly, AUC increased with stimulation intensity (Intensity: `r anova_print_Intensity_Post_AUC$statistic$stimStrength`; 100 vs 200 `r simple_print_Intensity_Post_AUC$statistic$X100_X200`, 200 vs 300 `r simple_print_Intensity_Post_AUC$statistic$X200_X300`), but was not modulated by drug condition (Drug: `r anova_print_Intensity_Post_AUC$statistic$drugs`, Drug x Intensity: `r anova_print_Intensity_Post_AUC$statistic$drugs_stimStrength`).

```{r 06_StimIntensity_Post DA_Latency_s, echo=FALSE,message = FALSE, include=FALSE, warning=FALSE}

#Filter the relevant stage of data for analysis
data_subset <- full_data %>% 
  filter(ExperimentalStage == "06_StimIntensity_Post")

anova <- aov_4(DA_Latency_s ~ drugs + (stimStrength|subj), data = data_subset, anova_table = list(correction = "none", es = "pes"))

anova_print_Intensity_Post_Latency <- apa_print(anova, mse = "FALSE",correction = "none",es = "pes")


simple <- emmeans(anova, ~stimStrength)
simple_print_Intensity_Post_Latency <- apa_print.emmGrid(pairs(simple, adjust = "tukey"))


```

Latency to peak was not modulated by stimulation intensity (Intensity: `r anova_print_Intensity_Post_Latency$statistic$stimStrength`, or by drug condition (Drug: `r anova_print_Intensity_Post_Latency$statistic$drugs`, Drug x Intensity: `r anova_print_Intensity_Post_Latency$statistic$drugs_stimStrength`).



### Stimulation Pulse Number Response Curve


```{r 07_StimPulses_Post DA_Max, echo=FALSE,message = FALSE, include=FALSE, warning=FALSE}

#Filter the relevant stage of data for analysis
data_subset <- full_data %>% 
  filter(ExperimentalStage == "07_StimPulses_Post")

anova <- aov_4(DA_max ~ drugs + (stimPulses|subj), data = data_subset, anova_table = list(correction = "none", es = "pes"))

anova_print_Pulses_Post_Peak <- apa_print(anova, mse = "FALSE",correction = "none",es = "pes")


simple <- emmeans(anova, ~stimPulses)
simple_print_Pulses_Post_Peak <- apa_print.emmGrid(pairs(simple, adjust = "tukey"))


```

Peak DA increased with pulse number (Pulses: `r anova_print_Pulses_Post_Peak$statistic$stimPulses`; 12 vs 24 `r simple_print_Pulses_Post_Peak$statistic$X12_X24`, 24 vs 36 `r simple_print_Pulses_Post_Peak$statistic$X24_X36`), but was not modulated by drug condition (Drug: `r anova_print_Pulses_Post_Peak$statistic$drugs`, Drug x Intensity: `r anova_print_Pulses_Post_Peak$statistic$drugs_stimPulses`).

```{r 07_StimPulses_Post DA_AUC, echo=FALSE,message = FALSE, include=FALSE, warning=FALSE}

#Filter the relevant stage of data for analysis
data_subset <- full_data %>% 
  filter(ExperimentalStage == "07_StimPulses_Post")

anova <- aov_4(DA_AUC ~ drugs + (stimPulses|subj), data = data_subset, anova_table = list(correction = "none", es = "pes"))

anova_print_Pulses_Post_AUC <- apa_print(anova, mse = "FALSE",correction = "none",es = "pes")


simple <- emmeans(anova, ~stimPulses)
simple_print_Pulses_Post_AUC <- apa_print.emmGrid(pairs(simple, adjust = "tukey"))


```

Similarly, AUC increased with stimulation intensity (Pulses: `r anova_print_Pulses_Post_AUC$statistic$stimPulses`; 12 vs 24 `r simple_print_Pulses_Post_AUC$statistic$X12_X24`, 24 vs 36 `r simple_print_Pulses_Post_AUC$statistic$X24_X36`), but was not modulated by drug condition (Drug: `r anova_print_Pulses_Post_AUC$statistic$drugs`, Drug x Intensity: `r anova_print_Pulses_Post_AUC$statistic$drugs_stimPulses`).

```{r 07_StimPulses_Post DA_Latency_s, echo=FALSE,message = FALSE, include=FALSE, warning=FALSE}

#Filter the relevant stage of data for analysis
data_subset <- full_data %>% 
  filter(ExperimentalStage == "07_StimPulses_Post")

anova <- aov_4(DA_Latency_s ~ drugs + (stimPulses|subj), data = data_subset, anova_table = list(correction = "none", es = "pes"))

anova_print_Pulses_Post_Latency <- apa_print(anova, mse = "FALSE",correction = "none",es = "pes")


simple <- emmeans(anova, ~stimPulses)
simple_print_Pulses_Post_Latency <- apa_print.emmGrid(pairs(simple, adjust = "tukey"))


```

Latency to peak was also modulated by stimulation intensity (Pulses: `r anova_print_Pulses_Post_Latency$statistic$stimPulses`; 12 vs 24 `r simple_print_Pulses_Post_Latency$statistic$X12_X24`, 24 vs 36 `r simple_print_Pulses_Post_Latency$statistic$X24_X36`), but was not modulated by drug condition (Drug: `r anova_print_Pulses_Post_Latency$statistic$drugs`, Drug x Intensity: `r anova_print_Pulses_Post_Latency$statistic$drugs_stimPulses`).



# Percent Baseline Data

## Pre Drug

### Stimulation Intensity Response Curve

```{r 02_StimIntensity_Pre DA_Max_PercBaseline, echo=FALSE,message = FALSE, include=FALSE, warning=FALSE}

#Filter the relevant stage of data for analysis
data_subset <- full_data %>% 
  filter(ExperimentalStage == "02_StimIntensity_Pre")

anova <- aov_4(DA_max_PercBaseline ~ drugs + (stimStrength|subj), data = data_subset, anova_table = list(correction = "none", es = "pes"))

anova_print <- apa_print(anova, mse = "FALSE",correction = "none",es = "pes")


simple <- emmeans(anova, ~stimStrength)
simple_print <- apa_print.emmGrid(pairs(simple, adjust = "tukey"))


```

Peak DA increased with stimulation intensity (Intensity: `r anova_print$statistic$stimStrength`; 100 vs 200 `r simple_print$statistic$X100_X200`, 200 vs 300 `r simple_print$statistic$X200_X300`), but was not modulated by drug condition (Drug: `r anova_print$statistic$drugs`, Drug x Intensity: `r anova_print$statistic$drugs_stimStrength`).

```{r 02_StimIntensity_Pre DA_AUC_PercBaseline, echo=FALSE,message = FALSE, include=FALSE, warning=FALSE}

#Filter the relevant stage of data for analysis
data_subset <- full_data %>% 
  filter(ExperimentalStage == "02_StimIntensity_Pre")

anova <- aov_4(DA_AUC_PercBaseline ~ drugs + (stimStrength|subj), data = data_subset, anova_table = list(correction = "none", es = "pes"))

anova_print <- apa_print(anova, mse = "FALSE",correction = "none",es = "pes")


simple <- emmeans(anova, ~stimStrength)
simple_print <- apa_print.emmGrid(pairs(simple, adjust = "tukey"))


```

Similarly, AUC increased with stimulation intensity (Intensity: `r anova_print$statistic$stimStrength`; 100 vs 200 `r simple_print$statistic$X100_X200`, 200 vs 300 `r simple_print$statistic$X200_X300`), but was not modulated by drug condition (Drug: `r anova_print$statistic$drugs`, Drug x Intensity: `r anova_print$statistic$drugs_stimStrength`).

```{r 02_StimIntensity_Pre DA_Latency_s_PercBaseline, echo=FALSE,message = FALSE, include=FALSE, warning=FALSE}

#Filter the relevant stage of data for analysis
data_subset <- full_data %>% 
  filter(ExperimentalStage == "02_StimIntensity_Pre")

anova <- aov_4(DA_Latency_s_PercBaseline ~ drugs + (stimStrength|subj), data = data_subset, anova_table = list(correction = "none", es = "pes"))

anova_print <- apa_print(anova, mse = "FALSE",correction = "none",es = "pes")


simple <- emmeans(anova, ~stimStrength)
simple_print <- apa_print.emmGrid(pairs(simple, adjust = "tukey"))


```

Latency to peak was not modulated by stimulation intensity (Intensity: `r anova_print$statistic$stimStrength`, or by drug condition (Drug: `r anova_print$statistic$drugs`, Drug x Intensity: `r anova_print$statistic$drugs_stimStrength`).



### Stimulation Pulse Number Response Curve


```{r 03_StimPulse_Pre DA_Max_PercBaseline, echo=FALSE,message = FALSE, include=FALSE, warning=FALSE}

#Filter the relevant stage of data for analysis
data_subset <- full_data %>% 
  filter(ExperimentalStage == "03_StimPulse_Pre")

anova <- aov_4(DA_max_PercBaseline ~ drugs + (stimPulses|subj), data = data_subset, anova_table = list(correction = "none", es = "pes"))

anova_print <- apa_print(anova, mse = "FALSE",correction = "none",es = "pes")


simple <- emmeans(anova, ~stimPulses)
simple_print <- apa_print.emmGrid(pairs(simple, adjust = "tukey"))


```

Peak DA increased with pulse number (Pulses: `r anova_print$statistic$stimPulses`; 12 vs 24 `r simple_print$statistic$X12_X24`, 24 vs 36 `r simple_print$statistic$X24_X36`), but was not modulated by drug condition (Drug: `r anova_print$statistic$drugs`, Drug x Intensity: `r anova_print$statistic$drugs_stimPulses`).

```{r 03_StimPulse_Pre DA_AUC_PercBaseline, echo=FALSE,message = FALSE, include=FALSE, warning=FALSE}

#Filter the relevant stage of data for analysis
data_subset <- full_data %>% 
  filter(ExperimentalStage == "03_StimPulse_Pre")

anova <- aov_4(DA_AUC_PercBaseline ~ drugs + (stimPulses|subj), data = data_subset, anova_table = list(correction = "none", es = "pes"))

anova_print <- apa_print(anova, mse = "FALSE",correction = "none",es = "pes")


simple <- emmeans(anova, ~stimPulses)
simple_print <- apa_print.emmGrid(pairs(simple, adjust = "tukey"))


```

Similarly, AUC increased with stimulation intensity (Pulses: `r anova_print$statistic$stimPulses`; 12 vs 24 `r simple_print$statistic$X12_X24`, 24 vs 36 `r simple_print$statistic$X24_X36`), but was not modulated by drug condition (Drug: `r anova_print$statistic$drugs`, Drug x Intensity: `r anova_print$statistic$drugs_stimPulses`).

```{r 03_StimPulse_Pre DA_Latency_s_PercBaseline, echo=FALSE,message = FALSE, include=FALSE, warning=FALSE}

#Filter the relevant stage of data for analysis
data_subset <- full_data %>% 
  filter(ExperimentalStage == "03_StimPulse_Pre")

anova <- aov_4(DA_Latency_s_PercBaseline ~ drugs + (stimPulses|subj), data = data_subset, anova_table = list(correction = "none", es = "pes"))

anova_print <- apa_print(anova, mse = "FALSE",correction = "none",es = "pes")


simple <- emmeans(anova, ~stimPulses)
simple_print <- apa_print.emmGrid(pairs(simple, adjust = "tukey"))


```

Latency to peak was also modulated by stimulation intensity (Pulses: `r anova_print$statistic$stimPulses`; 12 vs 24 `r simple_print$statistic$X12_X24`, 24 vs 36 `r simple_print$statistic$X24_X36`), but was not modulated by drug condition (Drug: `r anova_print$statistic$drugs`, Drug x Intensity: `r anova_print$statistic$drugs_stimPulses`).



## Post Drug

### Stimulation Intensity Response Curve

```{r 06_StimIntensity_Post DA_Max_PercBaseline, echo=FALSE,message = FALSE, include=FALSE, warning=FALSE}

#Filter the relevant stage of data for analysis
data_subset <- full_data %>% 
  filter(ExperimentalStage == "06_StimIntensity_Post")

anova <- aov_4(DA_max_PercBaseline ~ drugs + (stimStrength|subj), data = data_subset, anova_table = list(correction = "none", es = "pes"))

anova_print_Intenisty_Peak_Perc  <- apa_print(anova, mse = "FALSE",correction = "none",es = "pes")


simple <- emmeans(anova, ~stimStrength)
simple_print_Intenisty_Peak_Perc  <- apa_print.emmGrid(pairs(simple, adjust = "tukey"))


```

Peak DA increased with stimulation intensity (Intensity: `r anova_print_Intenisty_Peak_Perc$statistic$stimStrength`; 100 vs 200 `r simple_print_Intenisty_Peak_Perc$statistic$X100_X200`, 200 vs 300 `r simple_print_Intenisty_Peak_Perc$statistic$X200_X300`), but was not modulated by drug condition (Drug: `r anova_print_Intenisty_Peak_Perc$statistic$drugs`, Drug x Intensity: `r anova_print_Intenisty_Peak_Perc$statistic$drugs_stimStrength`).

```{r 06_StimIntensity_Post DA_AUC_PercBaseline, echo=FALSE,message = FALSE, include=FALSE, warning=FALSE}

#Filter the relevant stage of data for analysis
data_subset <- full_data %>% 
  filter(ExperimentalStage == "06_StimIntensity_Post")

anova <- aov_4(DA_AUC_PercBaseline ~ drugs + (stimStrength|subj), data = data_subset, anova_table = list(correction = "none", es = "pes"))

anova_print_Intenisty_AUC_Perc <- apa_print(anova, mse = "FALSE",correction = "none",es = "pes")


simple <- emmeans(anova, ~stimStrength)
simple_print_Intenisty_AUC_Perc <- apa_print.emmGrid(pairs(simple, adjust = "tukey"))


```

Similarly, AUC increased with stimulation intensity (Intensity: `r anova_print_Intenisty_AUC_Perc$statistic$stimStrength`; 100 vs 200 `r simple_print_Intenisty_AUC_Perc$statistic$X100_X200`, 200 vs 300 `r simple_print_Intenisty_AUC_Perc$statistic$X200_X300`), but was not modulated by drug condition (Drug: `r anova_print_Intenisty_AUC_Perc$statistic$drugs`, Drug x Intensity: `r anova_print_Intenisty_AUC_Perc$statistic$drugs_stimStrength`).

```{r 06_StimIntensity_Post DA_Latency_s_PercBaseline, echo=FALSE,message = FALSE, include=FALSE, warning=FALSE}

#Filter the relevant stage of data for analysis
data_subset <- full_data %>% 
  filter(ExperimentalStage == "06_StimIntensity_Post")

anova <- aov_4(DA_Latency_s_PercBaseline ~ drugs + (stimStrength|subj), data = data_subset, anova_table = list(correction = "none", es = "pes"))

anova_print_Intensity_Latency_Perc <- apa_print(anova, mse = "FALSE",correction = "none",es = "pes")


simple <- emmeans(anova, ~stimStrength)
simple_print_Intensity_Latency_Perc <- apa_print.emmGrid(pairs(simple, adjust = "tukey"))


```

Latency to peak was not modulated by stimulation intensity (Intensity: `r anova_print_Intensity_Latency_Perc$statistic$stimStrength`, or by drug condition (Drug: `r anova_print_Intensity_Latency_Perc$statistic$drugs`, Drug x Intensity: `r anova_print_Intensity_Latency_Perc$statistic$drugs_stimStrength`).



### Stimulation Pulse Number Response Curve


```{r 07_StimPulses_Post DA_Max_PercBaseline, echo=FALSE,message = FALSE, include=FALSE, warning=FALSE}

#Filter the relevant stage of data for analysis
data_subset <- full_data %>% 
  filter(ExperimentalStage == "07_StimPulses_Post")

anova <- aov_4(DA_max_PercBaseline ~ drugs + (stimPulses|subj), data = data_subset, anova_table = list(correction = "none", es = "pes"))

anova_print_Pulse_Peak_Perc <- apa_print(anova, mse = "FALSE",correction = "none",es = "pes")


simple <- emmeans(anova, ~stimPulses)
simple_print_Pulse_Peak_Perc <- apa_print.emmGrid(pairs(simple, adjust = "tukey"))


```

Peak DA increased with pulse number (Pulses: `r anova_print_Pulse_Peak_Perc$statistic$stimPulses`; 12 vs 24 `r simple_print_Pulse_Peak_Perc$statistic$X12_X24`, 24 vs 36 `r simple_print_Pulse_Peak_Perc$statistic$X24_X36`), but was not modulated by drug condition (Drug: `r anova_print_Pulse_Peak_Perc$statistic$drugs`, Drug x Intensity: `r anova_print_Pulse_Peak_Perc$statistic$drugs_stimPulses`).

```{r 07_StimPulses_Post DA_AUC_PercBaseline, echo=FALSE,message = FALSE, include=FALSE, warning=FALSE}

#Filter the relevant stage of data for analysis
data_subset <- full_data %>% 
  filter(ExperimentalStage == "07_StimPulses_Post")

anova <- aov_4(DA_AUC_PercBaseline ~ drugs + (stimPulses|subj), data = data_subset, anova_table = list(correction = "none", es = "pes"))

anova_print_Pulse_AUC_Perc <- apa_print(anova, mse = "FALSE",correction = "none",es = "pes")


simple <- emmeans(anova, ~stimPulses)
simple_print_Pulse_AUC_Perc  <- apa_print.emmGrid(pairs(simple, adjust = "tukey"))


```

Similarly, AUC increased with stimulation intensity (Pulses: `r anova_print_Pulse_AUC_Perc$statistic$stimPulses`; 12 vs 24 `r simple_print_Pulse_AUC_Perc$statistic$X12_X24`, 24 vs 36 `r simple_print_Pulse_AUC_Perc$statistic$X24_X36`), but was not modulated by drug condition (Drug: `r anova_print_Pulse_AUC_Perc$statistic$drugs`, Drug x Intensity: `r anova_print_Pulse_AUC_Perc$statistic$drugs_stimPulses`).

```{r 07_StimPulses_Post DA_Latency_s_PercBaseline, echo=FALSE,message = FALSE, include=FALSE, warning=FALSE}

#Filter the relevant stage of data for analysis
data_subset <- full_data %>% 
  filter(ExperimentalStage == "07_StimPulses_Post")

anova <- aov_4(DA_Latency_s_PercBaseline ~ drugs + (stimPulses|subj), data = data_subset, anova_table = list(correction = "none", es = "pes"))

anova_print_Pulse_Latency_Perc <- apa_print(anova, mse = "FALSE",correction = "none",es = "pes")


simple <- emmeans(anova, ~stimPulses)
simple_print_Pulse_Latency_Perc <- apa_print.emmGrid(pairs(simple, adjust = "tukey"))


```

Latency to peak was also modulated by stimulation intensity (Pulses: `r anova_print_Pulse_Latency_Perc$statistic$stimPulses`; 12 vs 24 `r simple_print_Pulse_Latency_Perc$statistic$X12_X24`, 24 vs 36 `r simple_print_Pulse_Latency_Perc$statistic$X24_X36`), but was not modulated by drug condition (Drug: `r anova_print_Pulse_Latency_Perc$statistic$drugs`, Drug x Intensity: `r anova_print_Pulse_Latency_Perc$statistic$drugs_stimPulses`).


